---
title: "Standardized PCR Analysis Script"
output: html_notebook
author: Cristina Banuelos
date: June 14, 1018
---


All PCR's were done by standardizing the coefficients (z-score) & using a 10-fold cross-validation

Standardization of variables
```{r}

baseline_p_scaled <- scale(mergedWINData$baseline_p)
baseline_q_scaled <- scale(mergedWINData$baseline_q)

density_baseline_scaled <- scale(mergedWINData$density_baseline)
clustering_coeff_average.binary._baseline_scaled <- scale(mergedWINData$clustering_coeff_average.binary._baseline)
transitivity.binary._baseline_scaled <- scale(mergedWINData$transitivity.binary._baseline)
network_characteristic_path_length.binary._baseline_scaled <- scale(mergedWINData$network_characteristic_path_length.binary._baseline)
small.worldness.binary._baseline_scaled <- scale(mergedWINData$small.worldness.binary._baseline)
global_efficiency.binary._baseline_scaled <- scale(mergedWINData$global_efficiency.binary._baseline)
local_efficiency.binary._baseline_scaled <- scale(mergedWINData$local_efficiency.binary._baseline)
assortativity_coefficient.binary._baseline_scaled <- scale(mergedWINData$assortativity_coefficient.binary._baseline)

transitivity.weighted._baseline_scaled <- scale(mergedWINData$transitivity.weighted._baseline)
network_characteristic_path_length.weighted._baseline_scaled <- scale(mergedWINData$network_characteristic_path_length.weighted._baseline)
small.worldness.weighted._baseline_scaled <- scale(mergedWINData$small.worldness.weighted._baseline)
global_efficiency.weighted._baseline_scaled <- scale(mergedWINData$global_efficiency.weighted._baseline)
local_efficiency.weighted._baseline_scaled <- scale(mergedWINData$local_efficiency.weighted._baseline)
assortativity_coefficient.weighted._baseline_scaled <- scale(mergedWINData$assortativity_coefficient.weighted._baseline)

standardizedVariables <- data.frame(density=density_baseline_scaled,
                                    clust_binary=clustering_coeff_average.binary._baseline_scaled,
                                    trans_binary=transitivity.binary._baseline_scaled,
                                    net_binary=network_characteristic_path_length.binary._baseline_scaled,
                                    small_binary=small.worldness.binary._baseline_scaled,
                                    global_binary=global_efficiency.binary._baseline_scaled,
                                    local_binary=local_efficiency.binary._baseline_scaled,
                                    assort_binary=assortativity_coefficient.binary._baseline_scaled,
                                    
                                    trans_weighted=transitivity.weighted._baseline_scaled,
                                    net_weighted=network_characteristic_path_length.weighted._baseline_scaled,
                                    small_weighted=small.worldness.weighted._baseline_scaled,
                                    global_weighted=global_efficiency.weighted._baseline_scaled,
                                    local_weighted=local_efficiency.weighted._baseline_scaled,
                                    assort_weighted=assortativity_coefficient.weighted._baseline_scaled,
                                    
                                    Pscore=baseline_p_scaled,
                                    Qscore=baseline_q_scaled)
```

#Binary (continuous) and P

1. Running PCR summary
2. Plotted the validation curve

```{r}
library(pls)

pcr.fit = pcr(baseline_p_scaled~
           density_baseline_scaled+
           clustering_coeff_average.binary._baseline_scaled+
           transitivity.binary._baseline_scaled+
           network_characteristic_path_length.binary._baseline_scaled+
           small.worldness.binary._baseline_scaled+
           global_efficiency.binary._baseline_scaled+
           local_efficiency.binary._baseline_scaled+
           assortativity_coefficient.binary._baseline_scaled,
          data = mergedWINData,
          scale = TRUE,
          validation = "CV"
           )

summary(pcr.fit)

validationplot(pcr.fit, val.type = "MSEP")
validationplot(pcr.fit, val.type = "R2")
predplot(pcr.fit)
coefplot(pcr.fit) # plot of regression coefficients
```

MODEL 



```{r}
set.seed(1)
x = standardizedVariables[,c(1,2,3,4,5,6,7,8)]
y = standardizedVariables$Pscore

train = sample(1:nrow(x), nrow(x))
test = (-train)
y.test = y[test]

  
pcr.pred = predict(na.exclude(pcr.fit), na.exclude(x[test,]), ncomp = 5)
mean(na.exclude(pcr.pred) - (na.exclude(y.test)^2))
```



#Binary (continuous) and Q

1. Running PCR summary
2. Plotted the validation curve
```{r}
library(pls)

pcr.fit = pcr(baseline_q_scaled~
           density_baseline_scaled+
           clustering_coeff_average.binary._baseline_scaled+
           transitivity.binary._baseline_scaled+
           network_characteristic_path_length.binary._baseline_scaled+
           small.worldness.binary._baseline_scaled+
           global_efficiency.binary._baseline_scaled+
           local_efficiency.binary._baseline_scaled+
           assortativity_coefficient.binary._baseline_scaled,
          data = mergedWINData,
          scale = TRUE,
          validation = "CV"
           )

summary(pcr.fit)

validationplot(pcr.fit, val.type = "MSEP")
validationplot(pcr.fit, val.type = "R2")
predplot(pcr.fit)
coefplot(pcr.fit)
```

#Weighted (continuous) and P

1. Running PCR summary
2. Plotted the validation curve

```{r}
library(pls)

pcr.fit = pcr(baseline_p_scaled~
           transitivity.weighted._baseline_scaled+
           network_characteristic_path_length.weighted._baseline_scaled+
           small.worldness.weighted._baseline_scaled+
           global_efficiency.weighted._baseline_scaled+
           local_efficiency.weighted._baseline_scaled+
           assortativity_coefficient.weighted._baseline_scaled,
          data = mergedWINData,
          scale = TRUE,
          validation = "CV"
           )

summary(pcr.fit)

validationplot(pcr.fit, val.type = "MSEP")
validationplot(pcr.fit, val.type = "R2")
predplot(pcr.fit)
coefplot(pcr.fit)
```


#Weighted (continuous) and Q

1. Running PCR summary
2. Plotted the validation curve

```{r}
library(pls)

pcr.fit = pcr(baseline_q_scaled~
           transitivity.weighted._baseline_scaled+
           network_characteristic_path_length.weighted._baselin e_scaled+
           small.worldness.weighted._baseline_scaled+
           global_efficiency.weighted._baseline_scaled+
           local_efficiency.weighted._baseline_scaled+
           assortativity_coefficient.weighted._baseline_scaled,
          data = mergedWINData,
          scale = TRUE,
          validation = "CV"
           )

summary(pcr.fit)

validationplot(pcr.fit, val.type = "MSEP")
validationplot(pcr.fit, val.type = "R2")
predplot(pcr.fit)
coefplot(pcr.fit)
```
