---
title: "WIN Data Correlation Script"
output: html_notebook
author: Cristy Banuelos
date: Friday, May 18, 2018
---

Baseline Variable data
Correlation Analysis between Network Measures & P/Q Scores

Part 1 - Binary Variables
Part 2 - Weighted/Continuous Variables 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

mergedWINData = read.csv(file="~/Desktop/mergedWINData.csv")
mergedWINData$X = NULL

```

----------------------------------------------------------------

Part 1 ~ Q Scores

Part 1 ~ P Scores

----------------------------------------------------------------
Density & P 

```{r}
cor(mergedWINData$density_baseline, mergedWINData$baseline_p, use ="pairwise.complete.obs")
```

Clustering Coefficient & P

```{r}
cor(mergedWINData$clustering_coeff_average.binary._baseline, mergedWINData$baseline_p, use ="pairwise.complete.obs")
```

Transitivity & P

```{r}
cor(mergedWINData$transitivity.binary._baseline, mergedWINData$baseline_p, use ="pairwise.complete.obs")
```

Network Characteristic Path Length & P

```{r}
cor(mergedWINData$network_characteristic_path_length.binary._baseline, mergedWINData$baseline_p, use ="pairwise.complete.obs")
```

Small Worldness & P

```{r}
cor(mergedWINData$small.worldness.binary._baseline, mergedWINData$baseline_p, use ="pairwise.complete.obs")
```

Global Efficiency & P

```{r}
cor(mergedWINData$global_efficiency.binary._baseline, mergedWINData$baseline_p, use ="pairwise.complete.obs")
```

Diameter of Graph & P 
Not numeric

```{r}
#cor(mergedWINData$diameter_of_graph.binary._baseline, mergedWINData$baseline_p, use ="pairwise.complete.obs")
```

Radius of Graph & P
Not numeric

```{r}
#cor(mergedWINData$radius_of_graph.binary._baseline, mergedWINData$baseline_p, use ="pairwise.complete.obs")
```

Local Efficiency & P

```{r}
cor(mergedWINData$local_efficiency.binary._baseline, mergedWINData$baseline_p, use ="pairwise.complete.obs")
```

Assortativity & P

```{r}
cor(mergedWINData$assortativity_coefficient.binary._baseline, mergedWINData$baseline_p, use ="pairwise.complete.obs")
```

----------------------------------------------------------------

Part 1 ~ Q Scores

----------------------------------------------------------------


Density & Q

```{r}
cor(mergedWINData$density_baseline, mergedWINData$baseline_q, use ="pairwise.complete.obs")
```


Clustering Coefficiency & Q

```{r}
cor(mergedWINData$clustering_coeff_average.binary._baseline, mergedWINData$baseline_q, use ="pairwise.complete.obs")
```

Transitivity & Q

```{r}
cor(mergedWINData$transitivity.binary._baseline, mergedWINData$baseline_q, use ="pairwise.complete.obs")
```

Network Characteristic Path Length & Q




















