---
title: "WIN Data Distribution Script"
output: html_document
author: Cristina Banuelos
date: May 15, 2018
---

Baseline Variable data
Distribution Analysis

Binary - summary table & boxplot (hidden)
Weighted/Continuous Variables - histogram 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

mergedWINData = read.csv(file="~/Desktop/mergedWINData.csv")
mergedWINData$X = NULL

```

Density 
- the fraction of present connections to all possible connections without taking into account any connection weights in the calculation (Rubinov & Sporns 2010)

```{r}
summary(mergedWINData$density_baseline)
#boxplot(mergedWINData$density_baseline)      
```

```{r}

hist(mergedWINData$density_baseline)
```

Clustering Coefficient Average
- alternative to transitivity

```{r}
summary(mergedWINData$clustering_coeff_average.binary._baseline)
#boxplot(mergedWINData$clustering_coeff_average.binary._baseline)      
```

```{r}
hist(mergedWINData$clustering_coeff_average.binary._baseline)
```


Transitivity
- the ratio of triangles to triplets in the network, and can be used as an alternative to the clustering coefficient (Rubinov & Sporns 2010)

```{r}
summary(mergedWINData$transitivity.binary._baseline)
#boxplot(mergedWINData$transitivity.binary._baseline)      
```

```{r}
summary(mergedWINData$transitivity.weighted._baseline)
hist(mergedWINData$transitivity.weighted._baseline)
```

(Network) Characteristic Path Length
- the average shortest path length in the network (Rubinov & Sporns) 
```{r}
summary(mergedWINData$network_characteristic_path_length.binary._baseline)
#boxplot(mergedWINData$network_characteristic_path_length.binary._baseline)      
```

```{r}
summary(mergedWINData$network_characteristic_path_length.weighted._baseline)
hist(mergedWINData$network_characteristic_path_length.weighted._baseline)
```

Small Worldness 
- dense local clustering or cliquishness of connections between neighboring nodes yet a short path length between any (distant) pair of nodes due to the existence of relatively few long range connections (Bassett & Bullmore 2006)

```{r}
summary(mergedWINData$small.worldness.binary._baseline)
#boxplot(mergedWINData$small.worldness.binary._baseline)      
```

```{r}
hist(mergedWINData$small.worldness.weighted._baseline)
```

Global Efficiency
- the average inverse shortest path length in the network (Rubinov & Sporns 2010)

```{r}
summary(mergedWINData$global_efficiency.binary._baseline)
#boxplot(mergedWINData$global_efficiency.binary._baseline)      
```

```{r}
hist(mergedWINData$global_efficiency.weighted._baseline)
```

Diameter of Graph 
- the maximum eccentricity (Rubinov & Sporns 2010)
```{r}
summary(mergedWINData$diameter_of_graph.binary._baseline)
#boxplot(mergedWINData$diameter_of_graph.binary._baseline)      
```

```{r}
hist(mergedWINData$diameter_of_graph.weighted._baseline)
```

Radius of Graph
- the minimum eccentricity (Rubinov & Sporns 2010)

```{r}
summary(mergedWINData$radius_of_graph.binary._baseline)
#boxplot(mergedWINData$radius_of_graph.binary._baseline)      
```

```{r}
hist(mergedWINData$radius_of_graph.weighted._baseline)
```

Local Efficiency 
-  the global efficiency computed on node neighborhoods, and is related to the clustering coefficient (Rubinov & Sporns 2010)

```{r}
summary(mergedWINData$local_efficiency.binary._baseline)
#boxplot(mergedWINData$local_efficiency.binary._baseline)      
```

```{r}
hist(mergedWINData$local_efficiency.weighted._baseline)
```

Assortativity
- a correlation coefficient between the degrees of all nodes on two opposite ends of a link (Rubinov & Sporns). A positive value would indicate that nodes tend to link to other nodes with the same or a similar degree (Rubinov & Sporns 2010).

```{r}
summary(mergedWINData$assortativity_coefficient.binary._baseline)
#boxplot(mergedWINData$assortativity_coefficient.binary._baseline)      
```

```{r}
hist(mergedWINData$assortativity_coefficient.weighted._baseline)
```







