---
title: "WIN Data Non-linear Correlation Script"
author: "Cristina Banuelos"
date: "June 1, 2018"
output:
  html_document:
    df_print: paged
---

All plots backwards - flip x & y


Baseline Variable data
Non-linear Correlation Analysis

Binary - Part 1

Weighted/Continuous Variables - Part 2

```{r setup, include=FALSE, echo=FALSE, error=FALSE}
library(ggplot2)
mergedWINData = read.csv(file="~/Desktop/mergedWINData.csv")
mergedWINData$X = NULL
```


--------------------------------------------------------------

Part 1 ~ P Scores

--------------------------------------------------------------


Density & P
```{r}
ggplot(data=mergedWINData, aes(y=baseline_p, x=density_baseline))+geom_smooth()+geom_point()

```

Clustering Coefficient & P
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$clustering_coeff_average.binary._baseline, x=baseline_p))+geom_smooth()+geom_point()
```

Transitivity & P
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$transitivity.binary._baseline, x=baseline_p))+geom_smooth()+geom_point()
```

Network Characteristic Path Length & P
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$network_characteristic_path_length.binary._baseline, x=baseline_p))+geom_smooth()+geom_point()
```

Small worldness & P
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$small.worldness.binary._baseline, x=baseline_p))+geom_smooth()+geom_point()
```

Global Efficiency & P
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$global_efficiency.binary._baseline, x=baseline_p))+geom_smooth()+geom_point()
```

No Diameter & P

No Redius  & P


Local Efficiency & P
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$local_efficiency.binary._baseline, x=baseline_p))+geom_smooth()+geom_point()
```

Assortativity Coefficient & P
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$assortativity_coefficient.binary._baseline, x=baseline_p))+geom_smooth()+geom_point()
```


--------------------------------------------------------------

Part 1 ~ Q Scores

--------------------------------------------------------------


Density & Q
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$density_baseline, x=baseline_q))+geom_smooth()+geom_point()
```

Clustering Coefficient & Q
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$clustering_coeff_average.binary._baseline, x=baseline_q))+geom_smooth()+geom_point()
```

Transitivity & Q
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$transitivity.binary._baseline, x=baseline_q))+geom_smooth()+geom_point()
```

Network Characteristic Path Length & Q
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$network_characteristic_path_length.binary._baseline, x=baseline_q))+geom_smooth()+geom_point()
```

Small Worldness & Q
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$small.worldness.binary._baseline, x=baseline_q))+geom_smooth()+geom_point()
```

Global Efficiency & Q
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$global_efficiency.binary._baseline, x=baseline_q))+geom_smooth()+geom_point()
```


No diameter & Q
No radius & Q



Local Efficiency & Q
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$local_efficiency.binary._baseline, x=baseline_q))+geom_smooth()+geom_point()
```

Assortativity & Q
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$assortativity_coefficient.binary._baseline, x=baseline_q))+geom_smooth()+geom_point()
```



--------------------------------------------------------------

Part 2 ~ P Scores

--------------------------------------------------------------

Transitivity & P
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$transitivity.weighted._baseline, x=baseline_p))+geom_smooth()+geom_point()
```


Network Characteristic Path Length & P
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$network_characteristic_path_length.weighted._baseline, x=baseline_p))+geom_smooth()+geom_point()
```

Small Worldness & P
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$small.worldness.weighted._baseline, x=baseline_p))+geom_smooth()+geom_point()
```

Global Efficiency & P
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$global_efficiency.weighted._baseline, x=baseline_p))+geom_smooth()+geom_point()
```

Diameter & P
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$diameter_of_graph.weighted._baseline, x=baseline_p))+geom_smooth()+geom_point()
```

Radius & P
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$radius_of_graph.weighted._baseline, x=baseline_p))+geom_smooth()+geom_point()
```

Local Efficiency & P
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$local_efficiency.weighted._baseline, x=baseline_p))+geom_smooth()+geom_point()
```

Assortativity & P
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$assortativity_coefficient.weighted._baseline, x=baseline_p))+geom_smooth()+geom_point()
```


--------------------------------------------------------------

Part 2 ~ Q Scores

--------------------------------------------------------------

Transitivity & Q
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$transitivity.weighted._baseline, x=baseline_q))+geom_smooth()+geom_point()
```

Network Characteristic Path Length & Q
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$network_characteristic_path_length.weighted._baseline, x=baseline_q))+geom_smooth()+geom_point()
```

Small Worldness & Q
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$small.worldness.weighted._baseline, x=baseline_q))+geom_smooth()+geom_point()
```


```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$global_efficiency.weighted._baseline, x=baseline_q))+geom_smooth()+geom_point()
```

Diameter & Q
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$diameter_of_graph.weighted._baseline, x=baseline_q))+geom_smooth()+geom_point()
```

Radius & Q
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$radius_of_graph.weighted._baseline, x=baseline_q))+geom_smooth()+geom_point()
```

Local Efficiency & Q
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$local_efficiency.weighted._baseline, x=baseline_q))+geom_smooth()+geom_point()
```

Assortativity & Q
```{r}
ggplot(data=mergedWINData, aes(y=mergedWINData$assortativity_coefficient.weighted._baseline, x=baseline_q))+geom_smooth()+geom_point()
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
